Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-10 manuscript/manuscript.tex
added dois
data availability statement
touch up

%\backmatter
\bmsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\bmsection*{Acknowledgments}
This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

\bmsection*{Data availability statement}

@@

\bmsection*{Ethics approval statement}

@@

\bmsection*{Supporting information}

Additional supporting information may be found in the
online version of the article at the publisher’s website.

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;

>>>>

%\backmatter

\bmsection*{Data availability statement}
The data and code used in the real data analysis and simulation
studies are publicly available in a GitHub repo:
\jy{Give the link}

@@

% \bmsection*{Ethics approval statement}

@@

% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
